RDF Validation Requirements - Evaluation and Logical Underpinning

### 2014-12-27 paper/RDF validation requirements/RDF validation requirements.tex
DL mappings added

\begin{itemize}
	\item Individual Value Restrictions: A has-value class expression ObjectHasValue( OPE a ) consists of an object property expression OPE and an individual a, and it contains all those individuals that are connected by OPE to a. Each such class expression can be seen as a syntactic shortcut for the class expression ObjectSomeValuesFrom( OPE ObjectOneOf( a ) ). 
	\item Literal Value Restrictions: A has-value class expression DataHasValue( DPE lt ) consists of a data property expression DPE and a literal lt, and it contains all those individuals that are connected by DPE to lt. Each such class expression can be seen as a syntactic shortcut for the class expression DataSomeValuesFrom( DPE DataOneOf( lt ) ).
\end{itemize}

@@

\begin{ex}
:Peter :fatherOf :Stewie . 
ObjectHasValue( :fatherOf :Stewie )
\end{ex}

\begin{itemize}
	\item The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie
  \item :Peter is classified as its instance
\end{itemize}

\begin{DL}
Not sure about the meaning of this constraint...\\
May be it is:\\
$Shortcut \sqsubseteq \exists fatherOf.\{\textbf{Stewie}\}$
\end{DL}

@@

\begin{itemize}
	\item A self-restriction ObjectHasSelf( OPE ) consists of an object property expression OPE, and it contains all those individuals that are connected by OPE to themselves. 
\end{itemize}

@@

\begin{ex}
:Peter :likes :Peter . 
ObjectHasSelf( :likes ) 
\end{ex}

@@

\begin{itemize}
	\item The self-restriction contains those individuals that like themselves
  \item :Peter is classified as its instance
\end{itemize}

@@

\begin{itemize}
  \item It is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets. 
\end{itemize}

\begin{itemize}
	\item Each object is uniquely identified by its social security number.
\end{itemize}

@@

\begin{itemize}
	\item The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN. 
\end{itemize}

@@

\begin{itemize}
	\item Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin . 
\end{itemize}

@@

@@

\begin{itemize}
  \item Some constraints require aggregating multiple values, especially via COUNT, MIN and MAX. 
\end{itemize}

>>>>

Individual Value Restrictions: A has-value class expression ObjectHasValue( OPE a ) consists of an object property expression OPE and an individual a, and it contains all those individuals that are connected by OPE to a. Each such class expression can be seen as a syntactic shortcut for the class expression ObjectSomeValuesFrom( OPE ObjectOneOf( a ) ). 
Literal Value Restrictions: A has-value class expression DataHasValue( DPE lt ) consists of a data property expression DPE and a literal lt, and it contains all those individuals that are connected by DPE to lt. Each such class expression can be seen as a syntactic shortcut for the class expression DataSomeValuesFrom( DPE DataOneOf( lt ) ).

@@

\begin{DL}
$FatherOfStewie \sqsubseteq \exists fatherOf.\{Stewie\}$
\end{DL}

\begin{ex}
# OWL 2
# -----
:Peter :fatherOf :Stewie . 
ObjectHasValue( :fatherOf :Stewie )
\end{ex}

The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie.
:Peter is classified as its instance.

\begin{gcotable}
property & FatherOfStewie & fatherOf & - & $\{Stewie\}$ & $\exists$ \\
\end{gcotable}

@@

A self-restriction ObjectHasSelf( OPE ) consists of an object property expression OPE, and it contains all those individuals that are connected by OPE to themselves.

@@

\begin{ex}
# OWL 2
# -----
:Peter :likes :Peter . 
ObjectHasSelf( :likes ) 
\end{ex}

@@

\begin{DL}
$\top$ $\sqsubseteq$ $\exists$ likes . Self
\end{DL}

\tb{my attempt}

\begin{gcotable}
property & $\exists$ likes . Self & likes & - & Self & $\exists$ \\
class & $\top$ & - & - & $\top$, $\exists$ likes . Self & $\sqsubseteq$ \\
\end{gcotable}

The self-restriction contains those individuals that like themselves.
:Peter is classified as its instance.

@@

It is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets.

\subsection{Simple Example}
Each object is uniquely identified by its social security number.

@@

The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN.

@@

Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin .

@@

\begin{DL}
$(\textsf{funct } \textsf{hasSSN})$
\end{DL}

\begin{gcotable}
property & $\top$ & hasSSN & - & - & functional & - \\
\end{gcotable}

\tb{my attempt}

@@

Some constraints require aggregating multiple values, especially via COUNT, MIN and MAX.
